### 2010-06-17 src/latex/bskernel_8cpp.tex
compressible branch

\hypertarget{boundary_8cpp}{
\section{boundary.cpp File Reference}
\label{boundary_8cpp}\index{boundary.cpp@{boundary.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for boundary.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{boundary_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{bskernel_8cpp}{
\section{bskernel.cpp File Reference}
\label{bskernel_8cpp}\index{bskernel.cpp@{bskernel.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for bskernel.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{bskernel_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/diagose_8cpp.tex
compressible branch

\hypertarget{bskernel_8cpp}{
\section{bskernel.cpp File Reference}
\label{bskernel_8cpp}\index{bskernel.cpp@{bskernel.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for bskernel.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{bskernel_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{diagose_8cpp}{
\section{diagose.cpp File Reference}
\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for diagose.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{diagose_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/force_8h.tex
compressible branch

\hypertarget{dllist_8h}{
\section{dllist.h File Reference}
\label{dllist_8h}\index{dllist.h@{dllist.h}}
}
Double linked list implementation.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{dllist_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$}
\begin{CompactList}\small\item\em A template node in the linked list. \item\end{CompactList}\item 
class \hyperlink{classLlist}{Llist$<$ Ldata $>$}
\begin{CompactList}\small\item\em Double linked list implementation. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Double linked list implementation.

\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$

changes by: Andreas Mattes Declares and defines a generic double linked list template \end{Desc}

>>>>

\hypertarget{force_8h}{
\section{force.h File Reference}
\label{force_8h}\index{force.h@{force.h}}
}
The class defining force on or between particles.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{force_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classForce}{Force}
\begin{CompactList}\small\item\em The class defining force on or between particles. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
The class defining force on or between particles.

### 2010-06-17 src/latex/hydrodynamics_8cpp.tex
compressible branch

\hypertarget{diagose_8cpp}{
\section{diagose.cpp File Reference}
\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for diagose.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{diagose_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{hydrodynamics_8cpp}{
\section{hydrodynamics.cpp File Reference}
\label{hydrodynamics_8cpp}\index{hydrodynamics.cpp@{hydrodynamics.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for hydrodynamics.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{hydrodynamics_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/initiation_8h.tex
compressible branch

\hypertarget{hydrodynamics_8h}{
\section{hydrodynamics.h File Reference}
\label{hydrodynamics_8h}\index{hydrodynamics.h@{hydrodynamics.h}}
}
Definition of materials and their hydrodynamical interactions.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{hydrodynamics_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classHydrodynamics}{Hydrodynamics}
\begin{CompactList}\small\item\em Definition of materials and their hydrodynamical interactions. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Definition of materials and their hydrodynamical interactions.

>>>>

\hypertarget{initiation_8h}{
\section{initiation.h File Reference}
\label{initiation_8h}\index{initiation.h@{initiation.h}}
}
Initiates the simulation.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{initiation_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classInitiation}{Initiation}
\begin{CompactList}\small\item\em Initiates the simulation. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Initiates the simulation.

### 2010-06-17 src/latex/interaction_8cpp.tex
compressible branch

\hypertarget{hydrodynamics_8cpp}{
\section{hydrodynamics.cpp File Reference}
\label{hydrodynamics_8cpp}\index{hydrodynamics.cpp@{hydrodynamics.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for hydrodynamics.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{hydrodynamics_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{interaction_8cpp}{
\section{interaction.cpp File Reference}
\label{interaction_8cpp}\index{interaction.cpp@{interaction.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for interaction.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{interaction_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/kernel_8cpp.tex
compressible branch

\hypertarget{dllist_8h}{
\section{dllist.h File Reference}
\label{dllist_8h}\index{dllist.h@{dllist.h}}
}
Double linked list implementation.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{dllist_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$}
\begin{CompactList}\small\item\em A template node in the linked list. \item\end{CompactList}\item 
class \hyperlink{classLlist}{Llist$<$ Ldata $>$}
\begin{CompactList}\small\item\em Double linked list implementation. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Double linked list implementation.

@@

changes by: Andreas Mattes Declares and defines a generic double linked list template \end{Desc}

>>>>

\hypertarget{kernel_8cpp}{
\section{kernel.cpp File Reference}
\label{kernel_8cpp}\index{kernel.cpp@{kernel.cpp}}
}
the abstract kernel base class

{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for kernel.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{kernel_8cpp__incl}
\end{center}
\end{figure}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
the abstract kernel base class

@@

changes by: Andreas Mattes \end{Desc}

### 2010-06-17 src/latex/material_8cpp.tex
compressible branch

\hypertarget{interaction_8cpp}{
\section{interaction.cpp File Reference}
\label{interaction_8cpp}\index{interaction.cpp@{interaction.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for interaction.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{interaction_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{material_8cpp}{
\section{material.cpp File Reference}
\label{material_8cpp}\index{material.cpp@{material.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for material.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{material_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/mls_8cpp.tex
compressible branch

\hypertarget{material_8cpp}{
\section{material.cpp File Reference}
\label{material_8cpp}\index{material.cpp@{material.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for material.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{material_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{mls_8cpp}{
\section{mls.cpp File Reference}
\label{mls_8cpp}\index{mls.cpp@{mls.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for mls.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{mls_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/output_8cpp.tex
compressible branch

\hypertarget{mls_8cpp}{
\section{mls.cpp File Reference}
\label{mls_8cpp}\index{mls.cpp@{mls.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for mls.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{mls_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{output_8cpp}{
\section{output.cpp File Reference}
\label{output_8cpp}\index{output.cpp@{output.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for output.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{output_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/particle_8cpp.tex
compressible branch

\hypertarget{output_8cpp}{
\section{output.cpp File Reference}
\label{output_8cpp}\index{output.cpp@{output.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for output.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{output_8cpp__incl}
\end{center}
\end{figure}

@@

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$, \end{Desc}

>>>>

\hypertarget{particle_8cpp}{
\section{particle.cpp File Reference}
\label{particle_8cpp}\index{particle.cpp@{particle.cpp}}
}
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for particle.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{particle_8cpp__incl}
\end{center}
\end{figure}

@@

changes by: \end{Desc}

### 2010-06-17 src/latex/quinticspline_8cpp.tex
compressible branch

\hypertarget{output_8cpp}{
\section{output.cpp File Reference}
\label{output_8cpp}\index{output.cpp@{output.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for output.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{output_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{quinticspline_8cpp}{
\section{quinticspline.cpp File Reference}
\label{quinticspline_8cpp}\index{quinticspline.cpp@{quinticspline.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for quinticspline.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{quinticspline_8cpp__incl}
\end{center}
\end{figure}

### 2010-06-17 src/latex/timesolver_8cpp.tex
compressible branch

\hypertarget{quinticspline_8cpp}{
\section{quinticspline.cpp File Reference}
\label{quinticspline_8cpp}\index{quinticspline.cpp@{quinticspline.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for quinticspline.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{quinticspline_8cpp__incl}
\end{center}
\end{figure}

>>>>

\hypertarget{timesolver_8cpp}{
\section{timesolver.cpp File Reference}
\label{timesolver_8cpp}\index{timesolver.cpp@{timesolver.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for timesolver.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{timesolver_8cpp__incl}
\end{center}
\end{figure}
